Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach

### 2019-12-11 main.tex
Completed my comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Result and discussion}\label{sec:result}
After the \ac{CNN} is trained, we can estimate its performance using the testing samples.
The results are presented in this section.
One of the most used and convenient ways to determine the classifying performance of a model is to plot the \ac{ROC} curve.
A \ac{ROC} shows the performance of a classifying model by showing the \ac{TAP} at a given \ac{FAP}. 
Since \ac{ROC} is usually plotted for model distinguishing two classes, 
for a multi-class classification problem, 
a \ac{ROC} for a class should be viewed as the class versus the others.
This means in this context, \ac{FAP} means the fraction of samples from other 
classes misidentified as a sample from the class the \ac{ROC} is associated with.
\ac{TAP} is identical to that of two-class classification problem and indicates the fraction of samples correctly identified.
For a given \ac{FAP}, a model with a higher \ac{TAP} is considered more capable than a model with a lower \ac{TAP}.
In Figure \ref{fig:ROClog}, we show the \acp{ROC} for both the mechanisms and \ac{GW} detector networks tested in this work. 
For simplicity, we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ROClog1}%
            \includegraphics[width=0.45\textwidth]{ROC_curves_neutrino.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ROClog2}
            \includegraphics[width=0.45\textwidth]{ROC_curves_mag.png}%
        }%
%
    \end{center}
    \caption{ROC curves showing the classification performance of the \ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three distances, $20$, $60$, and $100$kpc.
The left panel shows the results for the neutrino-driven mechanism, while the panel on the right shows those for the magnetorotational mechanism.
In both panels, the solid lines are for the network H+L+VK, while the dashed lines are for HLVK.
\label{fig:ROClog}}%
\end{figure*}
For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any given \acp{FAP} 
for magnetorotational than neutrino-driven signals.
That is not surprising as the amplitudes for magnetorotational signals are higher than that of neutrino-driven signals.

We can also show the classification efficiency of the \ac{CNN}  as a function of distance.
This is done by fixing the \ac{FAP} and plotting the \ac{TAP}. 
The results for three chosen \acp{FAP} are shown in Figure \ref{fig:eff}.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:eff1}%
            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}%
        }\quad
        \subfigure[]{%
            \label{fig:eff2}
            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the classification ability of the \ac{CNN} as a function of distance for both mechanisms and networks.
The left panel shows the results for the neutrino-driven mechanism, while the right shows those for the magnetorotational mechanism. 
In both panels, the solid lines show the results for the network H+L+VK, and the dashed lines for HLVK.
Three \acp{FAP} are chosen, i.e.: blue for \ac{FAP} $=0.1$, green for \ac{FAP} $=0.01$, red for \ac{FAP} $=0.001$.
\label{fig:eff}}%
\end{figure*}
In this figure, a similar trend is seen that magnetorotational signals are easier for the \ac{CNN} to identify than neutrino-driven signals at any distance. 
For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP} of $0.1$, 
the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the networks H+L+VK and HLVK respectively.
At more restrict \acp{FAP} such as $0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at the same distance for the two networks respectively.
For sources that are located at a slightly further distance of $60$ kpc, both networks achieve a \ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$.  
Such a range is well into the Large and Small Magellanic Clouds and covers the satellite galaxies in between\cite{karachentsev2004catalog, belokurov2007cats}.
For sources at $100$ kpc, the \acp{TAP} are close to or larger than $60\%$ for H+L+VK for all chosen \acp{FAP}, and is $73\%$ if the \ac{FAP} is $0.1$.  
Even for sources at $150$ and $200$ kpc, the \acp{TAP} are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with such a \ac{GW} network,
it is possible to detect magnetorotational \ac{CCSN} signals out to such a distance.
On the other hand, it is more difficult for the \ac{CNN} to detect and classify the neutrino-driven signals, due to their weaker amplitudes.
Nonetheless, for sources at $10$ kpc,
the \ac{CNN} achieves a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the \ac{FAP} is $0.1$.
This means that the \ac{GW} from a Galactic \ac{CCSN} signal is possible to be detected and classified with either of these networks.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ROCfixed1}%
            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ROCfixed2}
            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data with a fixed decision threshold(0.5), and their corresponding \acp{FAP}.
    The left panel shows the results for the neutrino-driven mechanism, and the right shows that for the magnetorotational mechanism.
    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the dashed lines show those for HLVK.  
\label{fig:ROCfixed}}%
\end{figure*}

In practice, since the output of a \ac{CNN} is probabilities indicating how likely the input belongs to each of the classes, 
it may be desired to set a threshold on which the decision whether the input belong to a class is made.
For example, an input will be classified into a class if the corresponding probability is larger than the pre-selected threshold.
In such a scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the threshold.
We show such a result in Figure \ref{fig:ROCfixed}, where we employed a threshold of $0.5$. 
For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. 
If the distance is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.
For the largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are $43\%$ and $29\%$ respectively.
For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and $80$ kpc respectively.
%The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
Throughout the distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for both networks.
For neutrino-driven signals, it is shown that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it is $55\%$ at $10$ kpc for HLVK.
Both of the networks have \acp{FAP} close to or less than $0.2$.
It should be noted that the results presented here are averaged over all the data samples in the testing samples.
The performance on any individual waveform may vary depending on the morphology and the amplitudes of the waveform.

@@

\section{Waveforms Excluded from Training}\label{sec:unseen}
The above section proves that using a \ac{CNN}, it is possible to detect and classify \ac{CCSN} waveforms 
if the waveforms have been used to train the \ac{CNN}. 
However, in reality, it is likely that the \acp{GW} from a \ac{CCSN} may only be partially similar to the simulated waveforms, 
while having some other features that are different or even unexpected. 
A \ac{CNN} that is only capable of recognising waveforms with which it is familiar may prove to be not entirely applicable.
Therefore, we apply our trained \ac{CNN} to waveforms from other studies that were not used during the training.
Similar to what was done in \cite{roma2019astrophysics}, 
we take the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from \cite{scheidegger2010influence} as the test waveforms for the magnetorotational mechanism.
The test waveforms for the neutrino-driven mechanisms are $\text{s}20$ from \cite{andresen2017gravitational} and $\text{SFHx}$ from \cite{kuroda2016new}.
The waveforms are shown in Figure \ref{fig:Extratestwaveform}.
The test waveforms in this section should not be confused with the testing samples in section \ref{sec:result}, 
which are randomly drawn from the same distribution as the training samples.
\begin{figure}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ex_waveform_neu}%
            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ex_waveform_mag}
            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}%
        }%
%
    \end{center}
    \caption{The waveforms excluded from the training session of the \ac{CNN} and used as an extra test for the performance of the \ac{CNN}.
    From the top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$(neutrino-driven mechanism), 
    $\text{R3E1AC}$ and $\text{R4E1FC\_L}$(magnetorotational mechanism), respectively. 
    The time in the x-axis is not related to core bounce.
\label{fig:Extratestwaveform}}%
\end{figure}
\begin{figure}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:extra_waveform_test_neu}%
            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}%
        }\quad
        \subfigure[]{%
            \label{fig:extra_waveform_test_mag}
            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data.
    The upper panel shows the results for the the waveforms $\text{SFHx}$ and $\text{s}20$ (neutrino-driven mechanism), 
    and the lower panel shows that for the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ (the magnetorotational mechanism).
    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for H+L+VK, and the dashed lines show those for HLVK.  
    The waveforms have not been used for the training of the \ac{CNN}.
\label{fig:Extratest}}%
\end{figure}
Using the procedure described in section \ref{sec:spwf}, we generate $1200$ injections for each distance and each class has around 400 injections.
The performance of the \ac{CNN} on the test waveforms are shown in Figure \ref{fig:Extratest}.
For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$ with H+L+VK and $59\%$ with HLVK respectively.
At $60$kpc, the \acp{TAP} drop slightly to $83\%$ and $52\%$ respectively.
This indicates that with the \ac{CNN}, it is possible to detect these waveforms from sources that are well into the Large and Small Magellanic Clouds.
For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$. 
The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably higher than that for the neutrino-driven mechanism in Figure \ref{fig:eff} for the same distance.
This is because as mentioned before, the detection and classification efficiency in Figure \ref{fig:eff} are the results averaged over the testing samples.
It is possible that individual waveforms may be easier for the \ac{CNN} to detect. The results indicate that the \ac{CNN} has generalised the features of the explosion mechanisms.
\section{Conclusion}\label{sec:conclusion}
We have demonstrated a \ac{CNN} can be applied for the purpose of distinguishing \ac{GW} detector time series 
among pure background noise and \ac{CCSN} explosion mechanisms. 
We trained the \ac{CNN} using $1.8\times10^{5}$ samples of simulated time series for each distance in a number of distances from $10$kpc to $200$kpc.
The data samples for each classes consisted of approximately $4\times10^5$ samples.

We have shown that with a network of HLVK, when the \ac{FAP} was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
for magnetorotational signals from sources at $60$ kpc. 
Using a network of H+L+VK, we showed that the \ac{TAP} could be even more promising at $91\%$. Both the Large and Small Magellanic Clouds are within this distance.
If the distance is extended to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ 
respectively are still achievable for H+L+VK, indicating the possibility of detections within such distances.

For the neutrino-driven mechanism, the weaker amplitudes of the waveforms result in lower \acp{TAP} at the same distances.
For sources at $10$kpc, the trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and $76\%$ for HLVK and H+L+VK respectively.
This indicates a Galactic \ac{CCSN} event is likely to be detectable.

We used four waveforms that were not used for the training of the \ac{CNN} to test the performance of the \ac{CNN} in a more realistic situation.
We found that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at $60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks respectively.
The results prove the possibility of using \ac{CNN} for the detection and classification of \ac{CCSN} \ac{GW} signals.
\\
\section*{ACKNOWLEDGEMENTS}
I.S.H. and C.M. are supported by
the Science and Technology Research Council (grant No.
ST/L000946/1) and the European Cooperation in
Science and Technology (COST) action CA17137. 
\bibliography{main}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Result and discussion}\label{sec:result}
%
% Introduction to the ROC results
%
After the \ac{CNN} is trained, we can estimate its performance using the
testing samples~\cm{what about the validation samples? These haven't been
motivated yet.} and the results of which are presented in this section. One of
the most commonly used and convenient ways to determine the classification
performance of a \ac{CNN} or equivelent signal detection algorithm is to plot
the \ac{ROC} curve. A \ac{ROC} shows the performance of a classifying model by
defining the \ac{TAP} as a function of the \ac{FAP}. Since \ac{ROC} curves are
usually plotted for models distinguishing between two classes, for a
multi-class classification problem, a \ac{ROC} for a class should be viewed as
the class versus the others. This means in this context, \ac{FAP} means the
fraction of samples from other classes misidentified as a sample from the class
the \ac{ROC} is associated with. The \ac{TAP} is identical to that of a
two-class classification problem and indicates the fraction of samples
correctly identified.  For a given \ac{FAP}, a model with a higher \ac{TAP} is
considered more capable than a model with a lower \ac{TAP}~\cm{it appears to me
that you haven't actually defined what your classification statistic is. Can
you make sure that the reader understands that how you go from the output of
the final sigmoid layer to making ROC curves. You have to define a detction
statistic.}.

%
% describe ROC curve plots (Fig 5)
%
In Fig.~\ref{fig:ROClog}, we show the \acp{ROC} for both of the \ac{CCSN}
mechanisms and \ac{GW} detector networks tested in this work. For simplicity,
we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any
given \acp{FAP} for magnetorotational than neutrino-driven signals.  That is
not surprising as the intrinsic amplitudes for magnetorotational signals are
higher than those of neutrino-driven signals~\cm{maybe a bit more description?
Maybe give some detection probabilities at standard FAP values in the text?}.

\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:ROClog1}
            \includegraphics[width=0.45\textwidth]{ROC_curves_neutrino.png}%
        }\quad
        \subfigure[]{
            \label{fig:ROClog2}
            \includegraphics[width=0.45\textwidth]{ROC_curves_mag.png}%
        }
    \end{center}
    \caption{\ac{ROC} curves showing the classification performance of the
\ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three
distances, $20$, $60$, and $100$kpc. The left panel shows the results for the
neutrino-driven mechanism, while the panel on the right shows those for the
magnetorotational mechanism. In both panels, the solid lines are for the
network H+L+VK, while the dashed lines are for HLVK.~\cm{please make these
plots square with equal length sides. Also add a diagonal line to indicate the
worst performance bound. Also make the y-axis scales the same for both plots or
at least highlight the fact that they are different in the text since it is
initially misleading. The legends don't need to have both solid and dashed
lines. Also add sub-labels indicateing that the left is magneto and the right
is neutrino.}\label{fig:ROClog}} 
\end{figure*}

%
% discuss the accuracy as a function of distance (Fig 6)
%
We also show the classification efficiency of the \ac{CNN}  as a function of
distance.  This is done by fixing the \ac{FAP} and plotting the \ac{TAP}.  The
results for three chosen \acp{FAP} values are shown in Fig.~\ref{fig:eff}.  In
this figure, a similar trend is seen that magnetorotational signals are easier
for the \ac{CNN} to identify than neutrino-driven signals at a given distance.
For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the
networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
$0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at
the same distance for the two networks respectively.  For sources that are
located at a slightly further distance of $60$ kpc, both networks achieve a
\ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$. Such a range
includes distances associated with the Large and Small Magellanic Clouds and
covers the satellite galaxies imbetween~\cite{karachentsev2004catalog,
belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are close to or
larger than $60\%$ for H+L+VK for all chosen \acp{FAP} values, and is $73\%$ if
the \ac{FAP} is $0.1$. Even for sources at $150$ and $200$ kpc, the \acp{TAP}
are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with
such a \ac{GW} network, it is possible to detect magnetorotational \ac{CCSN}
signals out to such a distance. On the other hand, it is more difficult for the
\ac{CNN} to detect and classify the neutrino-driven signals, due to their
weaker amplitudes. Nonetheless, for sources at $10$ kpc, the \ac{CNN} achieves
a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the
\ac{FAP} is $0.1$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
signal it is possible to detect and classify it with either of these \ac{GW}
detcetor networks.

%
% the TAP as a function of distance
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:eff1}
            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}
        }\quad
        \subfigure[]{
            \label{fig:eff2}
            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}
        }
    \end{center}
    \caption{Efficiency curves showing the classification ability of the
\ac{CNN} as a function of distance for both mechanisms and networks.  The left
panel shows the results for the neutrino-driven mechanism, while the right
shows those for the magnetorotational mechanism. In both panels, the solid
lines show the results for the network H+L+VK, and the dashed lines for HLVK.
Three \acp{FAP} values are chosen, blue for \ac{FAP} $=0.1$, green for \ac{FAP}
$=0.01$, red for \ac{FAP} $=0.001$.\label{fig:eff}}
\end{figure*}

%
% the TAP vs distance plot for fixed threshold
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:ROCfixed1}
            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}
        }\quad
        \subfigure[]{
            \label{fig:ROCfixed2}
            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}
        }
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in
distinguishing input data with a fixed decision threshold $(0.5)$~\cm{what is
this? Is it defined in the text?}, and their corresponding \acp{FAP}~\cm{and
TAP?}. The left panel shows the results for the neutrino-driven mechanism, and
the right shows that for the magnetorotational mechanism. In both panels, the
solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the
dashed lines show those for HLVK.\label{fig:ROCfixed}}
\end{figure*}

In practice, since the output of a \ac{CNN} is probabilities indicating how
likely the input belongs to each of the classes, it may be desired to set a
threshold on which the decision whether the input belong to a class is made.
For example, an input will be assigned into a certain class if the
corresponding probability is larger than the pre-selected threshold. In such a
scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the
threshold. We show such a result in Fig.~\ref{fig:ROCfixed}, where we employed
a threshold of $0.5$~\cm{I'm a bit confused. You have 3 classes so how exactly
are you doing this analysis? You mentioned before that you are treating one
class vs the remainder but when you talk about magneto does that mean that the
other model is noise AND neutrino. That would be strange.}. For H+L+VK and
magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. If the distance
is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.  For the
largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are
$43\%$ and $29\%$ respectively~\cm{these numbers don't seem to match the
plot.}. For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and
$80$ kpc respectively.
%The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for
both networks regarding magnetorotational waveforms. For neutrino-driven
signals, we show that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it
is $55\%$ at $10$ kpc for HLVK.  Both of the networks have \acp{FAP} close to
or less than $0.2$. It should be noted that the results presented here are
averaged over all the data samples in the testing samples. The performance on
any individual waveform may vary depending on the morphology and the amplitudes
of the waveform.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Waveforms Excluded from Training}\label{sec:unseen}
%
% introduce the issue of test samples from different families
%
The previous section proves that using a \ac{CNN}, it is possible to detect and
classify \ac{CCSN} waveforms if appropriate waveforms have been used to train
the \ac{CNN}. However, in reality, it is likely that the \acp{GW} from a
\ac{CCSN} may only be partially similar to the simulated waveforms, while
having some other features that are different or even unexpected. A \ac{CNN}
that is only capable of recognising waveforms with which it is familiar may
prove to be not be entirely applicable. Therefore, we apply our trained
\ac{CNN} to waveforms from other studies that were not used during the
training. Similar to the procedure used in~\cite{roma2019astrophysics}, we take
the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
from~\cite{scheidegger2010influence} as the test waveforms for the
magnetorotational mechanism. The test waveforms for the neutrino-driven
mechanisms are $\text{s}20$ from~\cite{andresen2017gravitational} and
$\text{SFHx}$ from~\cite{kuroda2016new}. Examples of these waveforms are shown
in Fig.~\ref{fig:Extratestwaveform}. The test waveforms in this section should
not be confused with the testing samples in Sec.~\ref{sec:result}, which are
randomly drawn from the same distribution as the training samples.

%
% plots of extra test waveforms
%
\begin{figure}
     \begin{center}
        \subfigure[]{
            \label{fig:ex_waveform_neu}
            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}
        }\quad
        \subfigure[]{
            \label{fig:ex_waveform_mag}
            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}
        }
    \end{center}
    \caption{The waveforms excluded from the training session of the \ac{CNN}
and used as an extra test for the performance of the trained \ac{CNN}. From the
top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$
(neutrino-driven mechanism), $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
(magnetorotational mechanism), respectively. The time in the x-axis is not
related to core bounce~\cm{again, why state this (same comment as for Fig.
2}.\label{fig:Extratestwaveform}} 
\end{figure}

%
% 
%
\begin{figure}
     \begin{center}
        \subfigure[]{
            \label{fig:extra_waveform_test_neu}
            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}
        }\quad
        \subfigure[]{
            \label{fig:extra_waveform_test_mag}
            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}
        }
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in
distinguishing input data.  The upper panel shows the results for the the
waveforms $\text{SFHx}$ and $\text{s}20$ (neutrino-driven mechanism), and the
lower panel shows that for the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
(the magnetorotational mechanism).  In both panels, the solid lines show the
\acp{TAP} and \acp{FAP} for H+L+VK, and the dashed lines show those for HLVK.
The waveforms have not been used for the training of the \ac{CNN}.
\label{fig:Extratest}}
\end{figure}

%
% the new test waveofmr procedure
%
Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1200$
injections~\cm{injections is jargon. Use the same terminolgy as used in the
rest of the paper} for each distance and therefore each class has $\sim 400$
injections. The performance of the \ac{CNN} on the test waveforms is shown in
Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$
with H+L+VK and $59\%$ with HLVK respectively. At $60$kpc, the \acp{TAP} drops
slightly to $83\%$ and $52\%$ respectively. This indicates that with the
\ac{CNN}, it is possible to detect these waveforms from sources that are at
distances consistent with the Large and Small Magellanic Clouds. For waveforms
$\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two
networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$.  The
efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
higher than that for the neutrino-driven mechanism in Fig.~\ref{fig:eff} for
the same distance. This is because as mentioned before, the detection and
classification efficiency in Fig.~\ref{fig:eff} are the results averaged over
the testing samples. It is possible that individual waveforms may be easier for
the \ac{CNN} to detect and the results here also indicate that the \ac{CNN} has
generalised the features of the explosion mechanisms.~\cm{this last statement
is very vague and needs clarification. What are features? and what does
generalisation mean in this context?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}
%
% overall main message
%
We have demonstrated that a \ac{CNN} can be applied for the purpose of
distinguishing \ac{GW} detector time-series among pure background noise and
\ac{CCSN} explosion mechanisms. We have trained the \ac{CNN} using
$1.8\times10^{5}$ samples of simulated time series for each distance at a
number of distances from $10$kpc to $200$kpc. The data samples for each
class consisted of approximately $4\times10^5$ samples.

%
% Primary magneto results
%
We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
for magnetorotational signals from sources at $60$ kpc. Using a network of
H+L+VK, we showed that the \ac{TAP} is imcreased to $91\%$.  Both the Large and
Small Magellanic Clouds are within this distance. If the distance is extended
to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ respectively are still
achievable for H+L+VK, indicating the small possibility of detections within
such distances.

%
% not so good neutrino results
%
For the neutrino-driven mechanism, the weaker amplitudes of the waveforms
result in lower \acp{TAP} at the same distances.  For sources at $10$kpc, the
trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and
$76\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
event would likely be detectable.

%
% statement about out of treaining data extra test samples
%
We used four waveforms that were not used for the training of the \ac{CNN} to
test the performance of the \ac{CNN} in a more realistic situation. We found
that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at
$60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and
$70\%$ for the two networks respectively. The results prove the possibility of
using a \ac{CNN} as a tool for the detection and classification of \ac{CCSN}
\ac{GW} signals.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGEMENTS}
%
%
%
I.S.H. and C.M. are supported by the Science and Technology Research Council
(grant No.~ST/L000946/1) and the European Cooperation in Science and
Technology (COST) action CA17137.

\bibliography{main}
